---
title: "R Markdown and Leaflet Assignment - Map of 10 Largest Capital Cities in the EU"
author: "Tomer Einhorn"
date: "8/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```


The following map contains pin points of the 10 most populated capital cities in the European Union.
Those cities are:
Berlin (Germany), Madrid (Spain), Rome (Italy), Paris (France), Bucharest (Romania), Vienna (Austria), Warsaw (Poland), Budapest (Hungary), Prague (Czech Republic), Sofia (Bulgaria).
The information was gathered from the following websites:

1. [Largest capital cities of the European Union](https://en.wikipedia.org/wiki/Largest_capital_cities_of_the_European_Union)

2. [List of Countries and Capitals](http://techslides.com/list-of-countries-and-capitals)

```{r}
library(leaflet)
europe_capitals <- data.frame(
        lat=c(52.51666667, 40.4, 41.9, 48.86666667, 44.43333333, 48.2, 52.25, 
              47.5, 50.08333333,42.68333333), 
        lng = c(13.4, -3.683333, 12.483333, 2.333333, 26.1, 16.366667, 21, 19.083333,
                14.466667, 23.316667))
capital_names <- c("Berlin (Germany)", "Madrid (Spain)", "Rome (Italy)", "Paris (France)", "Bucharest (Romania)", "Vienna (Austria)", "Warsaw (Poland)", "Budapest (Hungary)", "Prague (Czech Republic)", "Sofia (Bulgaria)")


leaflet(europe_capitals) %>% 
        addTiles() %>% 
        addMarkers(popup = capital_names)


```